### 2016-03-07 experiments.tex
Alex ready

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} clustering did not compare well with FPF, and the runtime was much worse than for FPF-based methods.  This tends to confirm earlier work's \cite{PLDI13} conclusion that clustering (at least based on X-means) simply does not work well in a setting with the kind of extreme disparity in instances of faults found in fuzzer taming.  A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

>>>>

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).
